\papertitle

### 2021-03-09 source_separation/paper/paper.tex
Edit conclusion

	\section{Conclusions}\label{sec:conclusions}
	In this paper, we addressed the problem of orchestrating dynamic targets using source separation as a preprocessing step. The results showed that performing source separation followed by a static orchestration of each individual sub targets improved the spectral distance between the original sample and its orchestrated version.

	Furthermore, it seems that unsupervised methods such as NMF outperform all supervised methods. However, it is important to notice that the different neural models (Demucs, ConvTasNet, ConvTasNetUniversal and OpenUnmix) were used based on pre-trained versions. Those versions were trained on musical data, except for TDCN++ which used selected generic sound samples, which opens a large path for improvement. More specifically, we may infer from our results that models trained not only on musical data can generate a better separation for orchestration, as TDCN++ outperforms other supervised models.

	Since unsupervised methods perform well, it is reasonable to think that supervised methods trained on a dataset well suited for source separation could yield better overall performances on dynamic orchestration.

>>>>

	\section{Conclusions}\label{sec:conclusions}
	In this paper, we addressed the problem of using source separation as a pre-processing step for computer-assisted orchestration. The results show that performing source separation followed by a static orchestration of each individual sub-target improved the spectral distance between the original target and its orchestrated version in three out of five of the methods tested.

	Furthermore, it seems that unsupervised methods, such as NMF, outperform all supervised methods tested. However, it is important to notice that the pre-trained version of the neural models (Demucs, TDCN, TDCN++ and OpenUnmix) were used. Except for TDCN++, these models were trained on musical data, yet we tested them on a wide range of targets, many of which were not strictly musical. More specifically, we may infer from our results that models trained on generic sounds generate a better separation for orchestration, as TDCN++ outperformed all other supervised models.

	Since unsupervised methods perform well, it is reasonable to think that supervised methods trained on a dataset of arbitrary sounds could yield better overall performance for orchestration.
